\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2021-11-16 doc/USER_MANUAL/06_fault_sources.tex
Buildbot ran the code beautifier.
Edits of User_Manual for adding exponential slip-weakening friction law

To facilitate the mesh generation with split nodes in CUBIT, we need
to separate the two fault surfaces by a small distance, effectively
creating a tiny opening of the fault (Figure \ref{fig:examples.splitnodes},
\ref{fig:examples.splitnodes-surfacetrace}). Note that the opening distance
should not be too small especially in single precision simulations
(For example, if your fault is at $y=y_0$ plane, then the opening distance
should be at least $10^{-6}y_0$ since single precision can ensure precision
within only 7 digits). Note that only the interior
of the fault must be opened, its edges must remain closed (except
the edge on the free surface). The fault is automatically closed later
by SPECFEM3D.\\

@@

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} /

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\end{description}

>>>>

To facilitate the mesh generation with split nodes in CUBIT, we need
to separate the two fault surfaces by a small distance, effectively
creating a tiny opening of the fault (Figure \ref{fig:examples.splitnodes},
\ref{fig:examples.splitnodes-surfacetrace}). Note that the opening distance
should not be too small especially in single precision simulations
(For example, if your fault is at $y=y_0$ plane, then the opening distance
should be at least $10^{-6}y_0$ since single precision can ensure precision
within only 7 digits; furthermore, to properly recognize split nodes, the dimension
of the mesh also affect numerical roundoffs, and therefore the split nodes
should also be at least \texttt{10.d-10 * (Xmax-Xmin)} apart). Note that only the interior
of the fault must be opened, its edges must remain closed (except
the edge on the free surface). The fault is automatically closed later
by SPECFEM3D.\\

@@

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} (weakening_kind=1 for linear (default); weakening_kind=2 for exponential)/

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\item [{weakening_kind}] = 1 for linear slip-weakening law (default); 2 for exponential slip-weakening law: $\mu_d + (\mu_s-\mu_d) \exp(-\frac{u}{d_c})$
\end{description}
